Local Group Satellite Alignments

### 2017-07-20 paper/paper.tex
caption

We find $11$ pairs with these conditions.
Figure \ref{fig:samples} shows the radial velocity versus distance for
the LGA pairs.

\begin{figure*}
\centering
\includegraphics[width=0.31\textwidth]{nsat.pdf}
\includegraphics[width=0.31\textwidth]{mstar.pdf}
\includegraphics[width=0.31\textwidth]{vmax.pdf}
\caption{Numer of satellites, stellar mass, vmax\label{fig:general}}
\end{figure*}
%\caption{Halo pair samples used in this paper located in the
%  plane of relative radial velocity $V_{r,AB}$ versus 
%  distance $R_{AB}$ between the two halos in the pair.
%  The IP sample (24 pairs) is a general pair sample, while the LGP
%  sample (12 pairs) resemples the separation and kinematic
%  conditions observed in the Local Group.}

>>>>

We find $11$ pairs with these conditions.
Figure \ref{fig:general} shows the stellar masses, maximum circular
velocities and the number of bright satellites for all the pairs in
the sample.

\begin{figure*}
\centering
\includegraphics[width=0.31\textwidth]{mstar.pdf}
\includegraphics[width=0.31\textwidth]{vmax.pdf}
\includegraphics[width=0.31\textwidth]{nsat.pdf}
\caption{Basic characteristics for the 11 pairs selected to be Local
  Group Analogues (circles). From left to right: stellar mass, maximum circular
  velocity and number of bright ($M_V<-9$) satellites.
  Galaxy A is the galaxy with the higher stellar mass.
  The squares represent the same characteristics for the observed
  Local Group. 
\label{fig:general}}
\end{figure*}
